External Patch Group Prior Guided Internal Orthogonal Dictionary Learning for Real Image Denoising

### 2016-10-23 CVPR2017_Review_Unified.tex
add

\subsection{Internal v.s. External Dictionary Learning}
For natural images, the internal patch recurrence across multiple scales has been successfully applied in many image restoration problems \cite{Irani2009sr,Irani2013separating,Irani2014deblur,Irani2016dehazing}. These work demonstrate that internal information is enough for many ill-posed problems including denoising additive white Gaussian noise. The rationale is, since the AWGN noise is independent of the original clean images, it will be reduced if the image is scaled to a smaller size. However, the noise in real images is generated mostly from the camera sensors, which is highly complex and signal dependent \cite{crosschannel2016}. Besides, according to the seminar workd of \cite{healey1994radiometric}, the noise in real images has fixed patterns from several main sources. Therefore, we can hardly seperate the complex noise from the signals without the help of external (correct) information of natural clean images. Only using the internal information may be not enough for real image denoising problem. On the other hand, the methods only using the external information may be not adaptive for real noisy images. Recently, the methods of \cite{mlp,csf,chen2015learning} had been proposed to learn, on both internal and external images, a process directly mapping the noisy patches to denoised ones. These discriminatice learning based methods are only effective on additive white Gaussian noise and ineffective on complex and signal dependent noise in real images. This has been shown in Figure \ref{fig1}. In this paper, our goal is to make use of external information to guide the subspace learning of internal PGs for image denoising task.

>>>>

\subsection{Internal v.s. External Dictionary Learning}
There are two categories of dictionary learning methods in image denoising. One category of methods \cite{epll,pgpd} learns dictionary from external clean images to reconstruct the given noisy images, while the other category of methods \cite{ple,ncsr} directly learns adaptive dictionary from the given noisy image to recover the latent clean image. The two categories of methods are very successful in removing Gaussian noise. However, the noise in real images is generated mostly from the camera sensors, which is highly complex and signal dependent \cite{crosschannel2016}. Besides, the noise in real images has fixed patterns from several main sources \cite{healey1994radiometric}. Therefore, we can hardly seperate the complex noise from the signals without the help of external (correct) information of natural clean images. In this paper, our goal is to employ the external patch group prior to guide the internal noisy PGs to be clustered into correct subspace, and the learning process of internal orthogonal dictionary.

%For natural images, the internal patch recurrence across multiple scales has been successfully applied in many image restoration problems \cite{Irani2009sr,Irani2013separating,Irani2014deblur,Irani2016dehazing}.
